Ensemble Stability of Biological Networks

### 2014-09-26 paper.tex
add figure showing symmetries under Hier

A strongly connected component of a graph is a maximal subset of vertices where each vertex within the subset can be reached from any other \cite{Cormen2009}. The strongly connected components of some examples of three component systems are outlined in \ref{fig:scc} along with their adjacency matrices and hierarchy diagrams (to be defined below).
The decomposition of a digraph into strongly connected components corresponds to a block triangular decomposition of its adjacency matrix.  Say that the graph $G$ has strongly connected components $C_1, C_2, \ldots C_n$, which have been labelled in such a way that there are no links from vertices in component $C_i$ to component $C_j$ when $i < j$.  Label the vertices in such a way that $v_1, \ldots, v_{n_1}$ belong to $C_1$, $v_{n_1 + 1}, \ldots, v_{n_2}$ belong to $C_2$, etc.  Then, if we choose basis vectors corresponding to this labelling of the vertices, we will have $a_{ij} = 0$ whenever $i$ and $j$ correspond to different components and $i > j$.  This condition is equivalent to stating that the matrix is block triangular with blocks of size $n_1, n_2, \ldots$.

@@

\todo{add figure showing all symmetries under $\hier$}
This map $\hier$ is many-to-one and so there is a large class of
operations which leaves $\hier(G)$ invariant for a given graph $G$.
For instance, we may interchange the positions of the strongly
connected components relative to each other.  Leaving the components
fixed, we may move links between nodes in a component or between
components, or even add or delete links.  Some examples of these
operations are illustrated in \ref{fig:scc}B and C.  As we shall see
later, some of these operations leave invariant key dynamical quantities, so
we may regard them as a symmetry groupoid of our system.

>>>>

A strongly connected component (SCC) of a graph is a maximal subset of vertices where each vertex within the subset can be reached from any other \cite{Cormen2009}. The strongly connected components of some examples of three component systems are outlined in \ref{fig:scc} along with their adjacency matrices and hierarchy diagrams (to be defined below).
The decomposition of a digraph into strongly connected components corresponds to a block triangular decomposition of its adjacency matrix.  Say that the graph $G$ has strongly connected components $C_1, C_2, \ldots C_n$, which have been labelled in such a way that there are no links from vertices in component $C_i$ to component $C_j$ when $i < j$.  Label the vertices in such a way that $v_1, \ldots, v_{n_1}$ belong to $C_1$, $v_{n_1 + 1}, \ldots, v_{n_2}$ belong to $C_2$, etc.  Then, if we choose basis vectors corresponding to this labelling of the vertices, we will have $a_{ij} = 0$ whenever $i$ and $j$ correspond to different components and $i > j$.  This condition is equivalent to stating that the matrix is block triangular with blocks of size $n_1, n_2, \ldots$.

@@

This map $\hier$ is many-to-one and so there is a large class of
operations which leaves $\hier(G)$ invariant for a given graph $G$.
For instance, we may interchange the positions of the strongly
connected components relative to each other \ref{fig:hiertransformations}A.  Leaving the components fixed, we may move links between nodes in a component \ref{fig:hiertransformations}B or between components, or even add or delete links \ref{fig:hiertransformations}C.  As we shall see later, some of these operations leave invariant key dynamical quantities, so we may regard them as a symmetry groupoid of our system.

### 2014-09-26 tex/figures.tex
add figure showing symmetries under Hier

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.7\columnwidth]{fig/connectcycle3D3x3.pdf}
\caption{{\bf Plot of stability to perturbations versus number of cycles and connectivity for three component systems.} }
\label{fig:connectcycle3D3x3}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.7\columnwidth]{fig/connectdist3D3x3.pdf}
\caption{{\bf Plot of robustness versus graph edit distance and connectivity for three component systems.} }
\label{fig:connectdist3D3x3}
\end{figure}

>>>>

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.7\columnwidth]{fig/hiertransformations.pdf}
\caption{{\bf Symmetries of the $\hier$ transformation between graphs and SCCs.} The transformation A represents an interchange of SCCs, B moving a link between nodes in a component and C adding a link. All three transformations represent symmetries of the $\hier$ transformation from graphs to SCCs while only A and B are symmetries of robustness.}
\label{fig:hiertransformations}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.7\columnwidth]{fig/connectcycle3D3x3.pdf}
\caption{{\bf Stability to perturbations versus number of cycles and connectivity for three component systems.} }
\label{fig:connectcycle3D3x3}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.7\columnwidth]{fig/connectdist3D3x3.pdf}
\caption{{\bf Robustness versus graph edit distance and connectivity for three component systems.} }
\label{fig:connectdist3D3x3}
\end{figure}
